Historical aerial surveys map long-term changes of forest cover and structure in the central Congo Basin

### 2020-01-23 manuscript/appendix.Rmd
revision

```{r echo=FALSE, out.width='100%', fig.cap="Overview of the complete flight plan of the survey around Kisangani (then Stanleyville) stored in the archives at the Africa Museum."}
knitr::include_graphics('./figures/flight_paths_overview.jpg')
```

```{r echo=FALSE, out.height='75%', fig.cap="Overview of the complete flight plan meta-data as stored in the archives at the Africa Museum."}
knitr::include_graphics('./figures/flight_paths_meta_data.jpg')
```

```{r echo=FALSE, out.height='50%', fig.cap="Boxplots comparing the first principal component (PC1) of a site based FOTO analysis across different forest types for both contemporary (Geo-Eye) and historical orthomosaic data."}
knitr::include_graphics('./figures/foto_bplot_psp.png')
```

```{r echo = FALSE, out.width="75%", eval = TRUE, fig.cap="Scatterplot comparing Above Ground Carbon and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly "}
knitr::include_graphics('./figures/foto_pc1_agc.png')
```

```{r echo = FALSE, out.width="75%", eval = TRUE, fig.cap="Scatterplot comparing tree species richness and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly"}
knitr::include_graphics('./figures/foto_pc1_diversity.png')
```

```{r echo = FALSE, out.width="75%", eval = TRUE, fig.cap="Scatterplot comparing stem density (per ha) and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly"}
knitr::include_graphics('./figures/foto_pc1_stems.png')
```

>>>>

```{r echo=FALSE, out.width='100%', fig.align="center", fig.cap="Overview of the complete flight plan of the survey around Kisangani (then Stanleyville) stored in the archives at the Africa Museum."}
knitr::include_graphics('./figures/flight_paths_overview.jpg')
```

```{r echo=FALSE, out.height='75%', fig.align="center", fig.cap="Overview of the complete flight plan meta-data as stored in the archives at the Africa Museum."}
knitr::include_graphics('./figures/flight_paths_meta_data.jpg')
```

```{r echo=FALSE, out.height='75%', fig.align="center",fig.cap="Shelves with aerial survey images at the Africa Museum archives."}
knitr::include_graphics('./figures/archives_aerial_photos_2.jpg')
```

```{r echo=FALSE, out.height='50%', fig.align="center",fig.cap="Boxplots comparing the first principal component (PC1) of a site based FOTO analysis across different forest types for both contemporary (Geo-Eye) and historical orthomosaic data."}
knitr::include_graphics('./figures/foto_bplot_psp.png')
```

```{r echo = FALSE, out.width="75%", fig.align="center",eval = TRUE, fig.cap="Scatterplot comparing Above Ground Carbon and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly "}
knitr::include_graphics('./figures/foto_pc1_agc.png')
```

```{r echo = FALSE, out.width="75%", fig.align="center",eval = TRUE, fig.cap="Scatterplot comparing tree species richness and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly"}
knitr::include_graphics('./figures/foto_pc1_diversity.png')
```

```{r echo = FALSE, out.width="75%", fig.align="center",eval = TRUE, fig.cap="Scatterplot comparing stem density (per ha) and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly"}
knitr::include_graphics('./figures/foto_pc1_stems.png')
```

### 2020-01-23 manuscript/appendix.tex
revision

\begin{figure}
\includegraphics[width=1\linewidth]{./figures/flight_paths_overview} \caption{Overview of the complete flight plan of the survey around Kisangani (then Stanleyville) stored in the archives at the Africa Museum.}\label{fig:unnamed-chunk-3}
\end{figure}

\begin{figure}
\includegraphics[width=82.67in,height=0.75\textheight]{./figures/flight_paths_meta_data} \caption{Overview of the complete flight plan meta-data as stored in the archives at the Africa Museum.}\label{fig:unnamed-chunk-4}
\end{figure}

\begin{figure}
\includegraphics[width=14.58in,height=0.5\textheight]{./figures/foto_bplot_psp} \caption{Boxplots comparing the first principal component (PC1) of a site based FOTO analysis across different forest types for both contemporary (Geo-Eye) and historical orthomosaic data.}\label{fig:unnamed-chunk-5}
\end{figure}

\begin{figure}
\includegraphics[width=0.75\linewidth]{./figures/foto_pc1_agc} \caption{Scatterplot comparing Above Ground Carbon and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly }\label{fig:unnamed-chunk-6}
\end{figure}

\begin{figure}
\includegraphics[width=0.75\linewidth]{./figures/foto_pc1_diversity} \caption{Scatterplot comparing tree species richness and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly}\label{fig:unnamed-chunk-7}
\end{figure}

\begin{figure}
\includegraphics[width=0.75\linewidth]{./figures/foto_pc1_stems} \caption{Scatterplot comparing stem density (per ha) and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly}\label{fig:unnamed-chunk-8}
\end{figure}

>>>>

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{./figures/flight_paths_overview}

}

\caption{Overview of the complete flight plan of the survey around Kisangani (then Stanleyville) stored in the archives at the Africa Museum.}\label{fig:unnamed-chunk-3}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=82.67in,height=0.75\textheight]{./figures/flight_paths_meta_data}

}

\caption{Overview of the complete flight plan meta-data as stored in the archives at the Africa Museum.}\label{fig:unnamed-chunk-4}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=14.39in,height=0.75\textheight]{./figures/archives_aerial_photos_2}

}

\caption{Shelves with aerial survey images at the Africa Museum archives.}\label{fig:unnamed-chunk-5}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=14.58in,height=0.5\textheight]{./figures/foto_bplot_psp}

}

\caption{Boxplots comparing the first principal component (PC1) of a site based FOTO analysis across different forest types for both contemporary (Geo-Eye) and historical orthomosaic data.}\label{fig:unnamed-chunk-6}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.75\linewidth]{./figures/foto_pc1_agc}

}

\caption{Scatterplot comparing Above Ground Carbon and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly }\label{fig:unnamed-chunk-7}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.75\linewidth]{./figures/foto_pc1_diversity}

}

\caption{Scatterplot comparing tree species richness and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly}\label{fig:unnamed-chunk-8}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=0.75\linewidth]{./figures/foto_pc1_stems}

}

\caption{Scatterplot comparing stem density (per ha) and the first principal component of the FOTO analysis for contemporary Geo-Eye (left) and the historical orthomosaic (right) data. Different forest types are plotted using closed circles, closed triangles, closed squares and this for fallow, mixed mon-dominant and young-regrowth forests, respectivelly}\label{fig:unnamed-chunk-9}
\end{figure}
